---
title: "Aid-Type Regressions: Growth and Health U5M"
author: "Ethan Sager"
format: pdf
header-includes:
    - \usepackage{pdflscape}
execute:
  echo: false
  message: false
  warning: false
code-fold: true
---

```{r setup}
if (!requireNamespace("pacman", quietly = TRUE)) {
    install.packages("pacman")
}

pacman::p_load(
    tidyverse,
    here,
    readr,
    fixest,
    zoo
)

options(scipen = 999)

# Default to 5-year panel data, but keep annual mode available.
panel_suffix <- "_5year"
window_label <- "5-year"
output_suffix <- if_else(panel_suffix == "", "_annual", panel_suffix)
period_label <- if_else(
    panel_suffix == "_5year",
    "Periods: 2005-09, 2010-14, 2015 endline",
    "Annual periods"
)

output_dir <- here::here("03_output", "tabs")
dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)

read_panel_csv <- function(file_stub) {
    file_path <- here::here(
        "01_panel_data",
        paste0(file_stub, panel_suffix, ".csv")
    )
    if (!file.exists(file_path)) {
        stop("Missing panel data file: ", file_path)
    }
    readr::read_csv(file_path, show_col_types = FALSE)
}

append_output_suffix <- function(file_name) {
    file_stub <- sub("\\.tex$", "", file_name)
    paste0(file_stub, output_suffix, ".tex")
}

table_title_with_window <- function(table_title) {
    paste0(table_title, " [", window_label, " panel; ", period_label, "]")
}

panel_aid_admin1 <- read_panel_csv("panel_aid_admin1_by_sector")
panel_aid_admin2 <- read_panel_csv("panel_aid_admin2_by_sector")

panel_aid_admin1_fin <- read_panel_csv("panel_aid_admin1_fin")
panel_aid_admin2_fin <- read_panel_csv("panel_aid_admin2_fin")

attach_iv <- function(sector_data, fin_data, key_cols) {
    sector_data %>%
        left_join(
            fin_data %>%
                select(all_of(c(key_cols, "IV_lag"))) %>%
                distinct(),
            by = key_cols
        )
}

prepare_panel_data <- function(data, admin_level) {
    if (admin_level == "GID_1") {
        data <- data %>%
            arrange(GID_1, study_group, year) %>%
            group_by(GID_1, study_group) %>%
            mutate(
                lag_mean_nl = dplyr::lag(mean_nl),
                nl_growth = case_when(
                    is.na(lag_mean_nl) ~ NA_real_,
                    TRUE ~
                        ((log(mean_nl + 0.01) - log(lag_mean_nl + 0.01)) /
                            log(lag_mean_nl + 0.01)) *
                            100
                ),
                lag_hhi_admin1 = dplyr::lag(frag_index_admin1),
                lag_pop_admin1 = dplyr::lag(ln_pop_admin1),
                lag_sgq_admin1 = dplyr::lag(mean_sgq_admin1),
                lag_donor_count_admin1 = dplyr::lag(donor_count_admin1),
                lag_total_proj_admin1 = dplyr::lag(total_proj_admin1),
                lag_total_aid_admin1 = log(dplyr::lag(total_aid_admin1) + 0.01)
            ) %>%
            ungroup()
    } else if (admin_level == "GID_2") {
        data <- data %>%
            arrange(GID_2, study_group, year) %>%
            group_by(GID_2, study_group) %>%
            mutate(
                lag_mean_nl = dplyr::lag(mean_nl),
                nl_growth = case_when(
                    is.na(lag_mean_nl) ~ NA_real_,
                    TRUE ~
                        ((log(mean_nl + 0.01) - log(lag_mean_nl + 0.01)) /
                            log(lag_mean_nl + 0.01)) *
                            100
                ),
                lag_hhi_admin2 = dplyr::lag(frag_index_admin2),
                lag_pop_admin2 = dplyr::lag(ln_pop_admin2),
                lag_sgq_admin2 = dplyr::lag(mean_sgq_admin2),
                lag_donor_count_admin2 = dplyr::lag(donor_count_admin2),
                lag_total_proj_admin2 = dplyr::lag(total_proj_admin2),
                lag_total_aid_admin2 = log(dplyr::lag(total_aid_admin2) + 0.01)
            ) %>%
            ungroup()
    } else {
        stop("admin_level must be either 'GID_1' or 'GID_2'")
    }

    data
}

harmonize_by_admin <- function(data, admin_level) {
    if (admin_level == "GID_1") {
        data <- data %>%
            mutate(
                total_aid = total_aid_admin1,
                frag_index = lag_hhi_admin1,
                lag_log_pop = lag_pop_admin1,
                lag_governance = lag_sgq_admin1,
                lag_donor_count = lag_donor_count_admin1,
                lag_total_proj = lag_total_proj_admin1,
                lag_total_aid = lag_total_aid_admin1
            )
    } else if (admin_level == "GID_2") {
        data <- data %>%
            mutate(
                total_aid = total_aid_admin2,
                frag_index = lag_hhi_admin2,
                lag_log_pop = lag_pop_admin2,
                lag_governance = lag_sgq_admin2,
                lag_donor_count = lag_donor_count_admin2,
                lag_total_proj = lag_total_proj_admin2,
                lag_total_aid = lag_total_aid_admin2
            )
    } else {
        stop("admin_level must be either 'GID_1' or 'GID_2'")
    }

    data
}

mark_governance_groups <- function(data, admin_level, high_cutoff = 0.75) {
    data <- harmonize_by_admin(data, admin_level)
    cutoff <- quantile(data$lag_governance, probs = high_cutoff, na.rm = TRUE)

    data %>%
        mutate(
            high_gov = if_else(
                !is.na(lag_governance) & lag_governance > cutoff,
                1L,
                0L,
                missing = 0L
            ),
            gov_group = if_else(high_gov == 1L, "high", "low")
        )
}

clean_outcome <- function(data, outcome_var) {
    data <- data %>%
        filter(!is.na(.data[[outcome_var]]), is.finite(.data[[outcome_var]]))

    if (outcome_var == "nl_growth" && nrow(data) > 0) {
        growth_cut <- quantile(
            data[[outcome_var]],
            probs = c(0.05, 0.95),
            na.rm = TRUE
        )
        data <- data %>%
            filter(
                .data[[outcome_var]] > growth_cut[[1]],
                .data[[outcome_var]] < growth_cut[[2]]
            )
    }

    data
}

center_governance_median <- function(data) {
    gov_median <- median(data$lag_governance, na.rm = TRUE)
    if (!is.finite(gov_median)) {
        gov_median <- 0
    }

    data %>%
        mutate(
            lag_governance_c = lag_governance - gov_median
        )
}

has_within_time_variation <- function(
    data,
    admin_level,
    required_vars = character(0)) {
    filtered <- data
    if (length(required_vars) > 0) {
        filtered <- filtered %>%
            filter(if_all(all_of(required_vars), ~ !is.na(.x) & is.finite(.x)))
    }

    counts <- filtered %>%
        distinct(.data[[admin_level]], year) %>%
        count(.data[[admin_level]], name = "n_years")

    if (nrow(counts) == 0) {
        return(FALSE)
    }

    any(counts$n_years >= 2)
}

fe_fallback_log <- tibble(
    context = character(),
    admin_level = character(),
    fe_term = character(),
    n_obs = integer(),
    n_units = integer(),
    min_year = double(),
    max_year = double()
)

resolve_fe_term <- function(
    data,
    admin_level,
    required_vars = character(0),
    context = "model") {
    if (has_within_time_variation(data, admin_level, required_vars)) {
        return(paste0("GID_0^year + ", admin_level))
    }

    fallback_entry <- tibble(
        context = context,
        admin_level = admin_level,
        fe_term = "GID_0",
        n_obs = nrow(data),
        n_units = dplyr::n_distinct(data[[admin_level]]),
        min_year = suppressWarnings(min(data$year, na.rm = TRUE)),
        max_year = suppressWarnings(max(data$year, na.rm = TRUE))
    )

    fe_fallback_log <<- bind_rows(fe_fallback_log, fallback_entry) %>%
        distinct()

    warning(
        paste0(
            "[",
            context,
            "] fallback to country FE (GID_0) due to insufficient within-",
            admin_level,
            " time variation."
        ),
        call. = FALSE
    )

    "GID_0"
}

perform_ols_analysis <- function(data, admin_level, outcome_var, cluster_var) {
    data <- harmonize_by_admin(data, admin_level) %>%
        clean_outcome(outcome_var)

    model_formula <- as.formula(
        paste0(outcome_var, " ~ frag_index + lag_total_aid + lag_log_pop")
    )

    fixest::feols(
        model_formula,
        cluster = as.formula(paste0("~", cluster_var)),
        data = data
    )
}

perform_fe_analysis <- function(data, admin_level, outcome_var, cluster_var) {
    data <- harmonize_by_admin(data, admin_level) %>%
        clean_outcome(outcome_var)

    fe_term <- resolve_fe_term(
        data,
        admin_level,
        c(outcome_var, "frag_index", "lag_total_aid", "lag_log_pop"),
        context = paste0("FE ", admin_level, " ", outcome_var)
    )

    model_formula <- as.formula(
        paste0(
            outcome_var,
            " ~ frag_index + lag_total_aid + lag_log_pop | ",
            fe_term
        )
    )

    fixest::feols(
        model_formula,
        cluster = as.formula(paste0("~", cluster_var)),
        data = data
    )
}

perform_cfa_analysis <- function(
    data,
    admin_level,
    outcome_var,
    iv_var,
    cluster_var) {
    data <- harmonize_by_admin(data, admin_level) %>%
        clean_outcome(outcome_var)

    fe_term <- resolve_fe_term(
        data,
        admin_level,
        c(
            "total_aid",
            iv_var,
            "lag_log_pop",
            outcome_var,
            "frag_index",
            "lag_total_aid"
        ),
        context = paste0("CFA ", admin_level, " ", outcome_var)
    )

    stage_1_formula <- as.formula(
        paste0(
            "total_aid ~ ",
            iv_var,
            " + lag_log_pop | ",
            fe_term
        )
    )

    stage_1 <- fixest::feols(
        stage_1_formula,
        cluster = as.formula(paste0("~", cluster_var)),
        data = data
    )

    data <- data %>%
        mutate(cfa = total_aid - predict(stage_1, newdata = data))

    stage_2_formula <- as.formula(
        paste0(
            outcome_var,
            " ~ frag_index + lag_total_aid + lag_log_pop + cfa | ",
            fe_term
        )
    )

    fixest::feols(
        stage_2_formula,
        cluster = as.formula(paste0("~", cluster_var)),
        data = data
    )
}

perform_interaction_ols_analysis <- function(
    data,
    admin_level,
    outcome_var,
    cluster_var) {
    data <- harmonize_by_admin(data, admin_level) %>%
        clean_outcome(outcome_var) %>%
        center_governance_median()

    model_formula <- as.formula(
        paste0(
            outcome_var,
            " ~ frag_index * lag_governance_c + lag_total_aid + lag_log_pop"
        )
    )

    fixest::feols(
        model_formula,
        cluster = as.formula(paste0("~", cluster_var)),
        data = data
    )
}

perform_interaction_fe_analysis <- function(
    data,
    admin_level,
    outcome_var,
    cluster_var) {
    data <- harmonize_by_admin(data, admin_level) %>%
        clean_outcome(outcome_var) %>%
        center_governance_median()

    fe_term <- resolve_fe_term(
        data,
        admin_level,
        c(
            outcome_var,
            "frag_index",
            "lag_governance_c",
            "lag_total_aid",
            "lag_log_pop"
        ),
        context = paste0("Interaction FE ", admin_level, " ", outcome_var)
    )

    model_formula <- as.formula(
        paste0(
            outcome_var,
            " ~ frag_index * lag_governance_c + lag_total_aid + lag_log_pop | ",
            fe_term
        )
    )

    fixest::feols(
        model_formula,
        cluster = as.formula(paste0("~", cluster_var)),
        data = data
    )
}

run_models_by_aid_type <- function(data, aid_types, model_runner) {
    results <- list()

    for (aid_type in aid_types) {
        aid_data <- data %>% filter(study_group == aid_type)

        fit <- tryCatch(
            model_runner(aid_data),
            error = function(e) {
                message(paste0("Skipped ", aid_type, ": ", e$message))
                NULL
            }
        )

        if (!is.null(fit)) {
            results[[aid_type]] <- fit
        }
    }

    results
}

build_dict <- function(include_cfa = FALSE, include_interaction = FALSE) {
    model_dict <- c(
        frag_index = "Lag Fragmentation",
        lag_total_aid = "Lag LN(Total Aid)",
        lag_log_pop = "Lag LN(Population)"
    )

    if (include_interaction) {
        model_dict <- c(
            model_dict,
            lag_governance_c = "Lag Governance (Median-Centered)",
            `frag_index:lag_governance_c` = "Lag Fragmentation x Lag Governance (Median-Centered)",
            lag_gov_variant_c = "Lag Governance (Spec-Centered)",
            `frag_index:lag_gov_variant_c` = "Lag Fragmentation x Lag Governance (Spec-Centered)"
        )
    }

    if (include_cfa) {
        model_dict <- c(model_dict, cfa = "CFA Residual")
    }

    model_dict
}

save_and_show_table <- function(
    model_list,
    file_name,
    include_cfa = FALSE,
    include_interaction = FALSE,
    headers = NULL,
    landscape = NULL,
    table_title = NULL) {
    if (length(model_list) == 0) {
        return(invisible(NULL))
    }

    if (is.null(headers)) {
        headers <- names(model_list)
    }

    if (is.null(landscape)) {
        landscape <- length(model_list) > 4
    }

    base_args <- c(
        model_list,
        list(
            headers = headers,
            dict = build_dict(include_cfa, include_interaction),
            digits = 4,
            placement = "H",
            se.below = TRUE,
            signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
            fitstat = c("n", "r2")
        )
    )

    if (!is.null(table_title)) {
        base_args <- c(
            base_args,
            list(title = table_title_with_window(table_title))
        )
    }

    do.call(
        fixest::etable,
        c(
            base_args,
            list(
                tex = TRUE,
                file = here::here(
                    "03_output",
                    "tabs",
                    append_output_suffix(file_name)
                )
            )
        )
    )

    latex_table <- do.call(fixest::etable, c(base_args, list(tex = TRUE)))

    if (isTRUE(landscape)) {
        cat("\\begin{landscape}\n")
        cat(latex_table, sep = "\n")
        cat("\n")
        cat("\\end{landscape}\n\n")
    } else {
        cat(latex_table, sep = "\n")
        cat("\n\n")
    }

    invisible(latex_table)
}

safe_num <- function(
    x,
    stat = c("mean", "median", "min", "max", "q25", "q75")) {
    stat <- match.arg(stat)
    x <- x[is.finite(x)]
    if (length(x) == 0) {
        return(NA_real_)
    }

    if (stat == "mean") {
        return(mean(x))
    }
    if (stat == "median") {
        return(median(x))
    }
    if (stat == "min") {
        return(min(x))
    }
    if (stat == "max") {
        return(max(x))
    }
    if (stat == "q25") {
        return(as.numeric(quantile(x, 0.25, na.rm = TRUE)))
    }

    as.numeric(quantile(x, 0.75, na.rm = TRUE))
}

safe_cor <- function(x, y) {
    keep <- is.finite(x) & is.finite(y)
    if (sum(keep) < 2) {
        return(NA_real_)
    }
    cor(x[keep], y[keep])
}

compute_stability_metrics <- function(
    data,
    id_var,
    sgq_var,
    source_label,
    small_delta = 2) {
    d <- data %>%
        select(id = all_of(id_var), year, sgq = all_of(sgq_var)) %>%
        filter(!is.na(id), !is.na(year), is.finite(sgq)) %>%
        arrange(id, year)

    if (nrow(d) == 0) {
        return(tibble(
            source = source_label,
            units = NA_integer_,
            rows = NA_integer_,
            year_min = NA_real_,
            year_max = NA_real_,
            lag_corr = NA_real_,
            transition_persistence = NA_real_,
            median_abs_change = NA_real_,
            share_small_change = NA_real_,
            slope_p25 = NA_real_,
            slope_median = NA_real_,
            slope_p75 = NA_real_,
            median_gap_years = NA_real_
        ))
    }

    cutoff <- quantile(d$sgq, probs = 0.75, na.rm = TRUE)

    lag_data <- d %>%
        group_by(id) %>%
        mutate(
            lag_sgq = dplyr::lag(sgq),
            delta = sgq - lag_sgq,
            gap = year - dplyr::lag(year),
            high = sgq > cutoff,
            high_lag = dplyr::lag(high)
        ) %>%
        ungroup()

    lag_pairs <- lag_data %>%
        filter(is.finite(lag_sgq), is.finite(delta), is.finite(gap))

    slope_data <- d %>%
        group_by(id) %>%
        filter(n() >= 3) %>%
        summarise(
            slope = coef(lm(sgq ~ year))[2],
            .groups = "drop"
        )

    tibble(
        source = source_label,
        units = n_distinct(d$id),
        rows = nrow(d),
        year_min = safe_num(d$year, "min"),
        year_max = safe_num(d$year, "max"),
        lag_corr = safe_cor(lag_pairs$sgq, lag_pairs$lag_sgq),
        transition_persistence = safe_num(
            as.numeric(lag_pairs$high == lag_pairs$high_lag),
            "mean"
        ),
        median_abs_change = safe_num(abs(lag_pairs$delta), "median"),
        share_small_change = safe_num(
            as.numeric(abs(lag_pairs$delta) <= small_delta),
            "mean"
        ),
        slope_p25 = safe_num(slope_data$slope, "q25"),
        slope_median = safe_num(slope_data$slope, "median"),
        slope_p75 = safe_num(slope_data$slope, "q75"),
        median_gap_years = safe_num(lag_pairs$gap, "median")
    )
}

predict_bounded_trend <- function(year_vec, observed_vec, baseline_vec) {
    keep <- is.finite(observed_vec)

    if (sum(keep) >= 2) {
        fit <- lm(
            y ~ t,
            data = tibble(y = observed_vec[keep], t = year_vec[keep])
        )
        pred <- as.numeric(predict(fit, newdata = tibble(t = year_vec)))
        lo <- min(observed_vec[keep], na.rm = TRUE)
        hi <- max(observed_vec[keep], na.rm = TRUE)
        pred <- pmin(pmax(pred, lo), hi)
        return(if_else(is.na(pred), baseline_vec, pred))
    }

    if (sum(keep) == 1) {
        return(rep(observed_vec[keep][1], length(year_vec)))
    }

    baseline_vec
}

build_governance_paths <- function(panel_data, admin_level, observed_lookup) {
    sgq_var <- if_else(
        admin_level == "GID_1",
        "mean_sgq_admin1",
        "mean_sgq_admin2"
    )

    panel_data %>%
        select(all_of(c(admin_level, "year", sgq_var))) %>%
        distinct() %>%
        left_join(observed_lookup, by = c(admin_level, "year")) %>%
        arrange(.data[[admin_level]], year) %>%
        group_by(.data[[admin_level]]) %>%
        mutate(
            sgq_baseline = .data[[sgq_var]],
            sgq_cf = zoo::na.locf(sgq_observed, na.rm = FALSE),
            sgq_cf = zoo::na.locf(sgq_cf, na.rm = FALSE, fromLast = TRUE),
            sgq_cf = if_else(is.na(sgq_cf), sgq_baseline, sgq_cf),
            sgq_trend = predict_bounded_trend(year, sgq_observed, sgq_baseline),
            lag_gov_baseline = dplyr::lag(sgq_baseline),
            lag_gov_cf = dplyr::lag(sgq_cf),
            lag_gov_trend = dplyr::lag(sgq_trend)
        ) %>%
        ungroup() %>%
        select(
            all_of(admin_level),
            year,
            lag_gov_baseline,
            lag_gov_cf,
            lag_gov_trend
        )
}

run_variant_interaction <- function(
    data,
    admin_level,
    outcome_var,
    cluster_var,
    lag_var) {
    d <- harmonize_by_admin(data, admin_level) %>%
        clean_outcome(outcome_var) %>%
        mutate(lag_gov_variant = .data[[lag_var]]) %>%
        filter(!is.na(lag_gov_variant), is.finite(lag_gov_variant))

    if (nrow(d) == 0) {
        return(NULL)
    }

    gov_center <- median(d$lag_gov_variant, na.rm = TRUE)
    if (!is.finite(gov_center)) {
        gov_center <- 0
    }

    d <- d %>%
        mutate(lag_gov_variant_c = lag_gov_variant - gov_center)

    fixest::feols(
        as.formula(
            paste0(
                outcome_var,
                " ~ frag_index * lag_gov_variant_c + lag_total_aid + lag_log_pop"
            )
        ),
        cluster = as.formula(paste0("~", cluster_var)),
        data = d
    )
}

collect_sensitivity_terms <- function(model_list, admin_label) {
    purrr::imap_dfr(model_list, function(model, spec_name) {
        if (is.null(model)) {
            return(tibble())
        }

        ct <- fixest::coeftable(model)
        tibble(
            admin = admin_label,
            spec = spec_name,
            term = rownames(ct),
            estimate = ct[, 1],
            std_error = ct[, 2],
            p_value = ct[, 4]
        ) %>%
            filter(
                term %in%
                    c(
                        "frag_index",
                        "lag_gov_variant_c",
                        "frag_index:lag_gov_variant_c"
                    )
            )
    })
}

panel_aid_admin1 <- attach_iv(
    panel_aid_admin1,
    panel_aid_admin1_fin,
    c("GID_0", "GID_1", "year")
) %>%
    prepare_panel_data("GID_1") %>%
    mark_governance_groups("GID_1")

panel_aid_admin2 <- attach_iv(
    panel_aid_admin2,
    panel_aid_admin2_fin,
    c("GID_0", "GID_1", "GID_2", "year")
) %>%
    prepare_panel_data("GID_2") %>%
    mark_governance_groups("GID_2")

aid_types <- sort(unique(panel_aid_admin1$study_group))
```

## Setup diagnostics

```{r setup_diagnostics}
loaded_panel_diagnostics <- tibble(
    dataset = c(
        "panel_aid_admin1_by_sector",
        "panel_aid_admin2_by_sector",
        "panel_aid_admin1_fin",
        "panel_aid_admin2_fin",
        "analysis_panel_admin1",
        "analysis_panel_admin2"
    ),
    rows = c(
        nrow(read_panel_csv("panel_aid_admin1_by_sector")),
        nrow(read_panel_csv("panel_aid_admin2_by_sector")),
        nrow(read_panel_csv("panel_aid_admin1_fin")),
        nrow(read_panel_csv("panel_aid_admin2_fin")),
        nrow(panel_aid_admin1),
        nrow(panel_aid_admin2)
    ),
    years = c(
        paste(
            sort(unique(read_panel_csv("panel_aid_admin1_by_sector")$year)),
            collapse = ", "
        ),
        paste(
            sort(unique(read_panel_csv("panel_aid_admin2_by_sector")$year)),
            collapse = ", "
        ),
        paste(
            sort(unique(read_panel_csv("panel_aid_admin1_fin")$year)),
            collapse = ", "
        ),
        paste(
            sort(unique(read_panel_csv("panel_aid_admin2_fin")$year)),
            collapse = ", "
        ),
        paste(sort(unique(panel_aid_admin1$year)), collapse = ", "),
        paste(sort(unique(panel_aid_admin2$year)), collapse = ", ")
    )
)

analysis_retention <- tibble(
    metric = c(
        "Rows with non-missing nl_growth (admin1)",
        "Rows with non-missing nl_growth (admin2)",
        "Aid types retained"
    ),
    value = c(
        as.character(sum(
            !is.na(panel_aid_admin1$nl_growth) &
                is.finite(panel_aid_admin1$nl_growth)
        )),
        as.character(sum(
            !is.na(panel_aid_admin2$nl_growth) &
                is.finite(panel_aid_admin2$nl_growth)
        )),
        paste(aid_types, collapse = ", ")
    )
)

knitr::kable(loaded_panel_diagnostics, digits = 3)
cat("\n")
knitr::kable(analysis_retention, digits = 3)
```

## 1) Split sample: high vs low governance, by aid type (growth)

```{r split_growth, results='asis'}
high_admin1 <- panel_aid_admin1 %>% filter(high_gov == 1L)
low_admin1 <- panel_aid_admin1 %>% filter(high_gov == 0L)
high_admin2 <- panel_aid_admin2 %>% filter(high_gov == 1L)
low_admin2 <- panel_aid_admin2 %>% filter(high_gov == 0L)

# OLS
ols_high_admin1 <- run_models_by_aid_type(
    high_admin1,
    aid_types,
    function(df) perform_ols_analysis(df, "GID_1", "nl_growth", "GID_0")
)
ols_low_admin1 <- run_models_by_aid_type(
    low_admin1,
    aid_types,
    function(df) perform_ols_analysis(df, "GID_1", "nl_growth", "GID_0")
)
ols_high_admin2 <- run_models_by_aid_type(
    high_admin2,
    aid_types,
    function(df) perform_ols_analysis(df, "GID_2", "nl_growth", "GID_0")
)
ols_low_admin2 <- run_models_by_aid_type(
    low_admin2,
    aid_types,
    function(df) perform_ols_analysis(df, "GID_2", "nl_growth", "GID_0")
)

save_and_show_table(
    ols_high_admin1,
    "aidtype_ols_growth_admin1_highgov.tex",
    table_title = "Table 1A. OLS Growth Models by Aid Type: Admin1, High Governance"
)
save_and_show_table(
    ols_low_admin1,
    "aidtype_ols_growth_admin1_lowgov.tex",
    table_title = "Table 1B. OLS Growth Models by Aid Type: Admin1, Low Governance"
)
save_and_show_table(
    ols_high_admin2,
    "aidtype_ols_growth_admin2_highgov.tex",
    table_title = "Table 1C. OLS Growth Models by Aid Type: Admin2, High Governance"
)
save_and_show_table(
    ols_low_admin2,
    "aidtype_ols_growth_admin2_lowgov.tex",
    table_title = "Table 1D. OLS Growth Models by Aid Type: Admin2, Low Governance"
)

# FE
fe_high_admin1 <- run_models_by_aid_type(
    high_admin1,
    aid_types,
    function(df) perform_fe_analysis(df, "GID_1", "nl_growth", "GID_0")
)
fe_low_admin1 <- run_models_by_aid_type(
    low_admin1,
    aid_types,
    function(df) perform_fe_analysis(df, "GID_1", "nl_growth", "GID_0")
)
fe_high_admin2 <- run_models_by_aid_type(
    high_admin2,
    aid_types,
    function(df) perform_fe_analysis(df, "GID_2", "nl_growth", "GID_0")
)
fe_low_admin2 <- run_models_by_aid_type(
    low_admin2,
    aid_types,
    function(df) perform_fe_analysis(df, "GID_2", "nl_growth", "GID_0")
)

save_and_show_table(
    fe_high_admin1,
    "aidtype_fe_growth_admin1_highgov.tex",
    table_title = "Table 2A. FE Growth Models by Aid Type: Admin1, High Governance"
)
save_and_show_table(
    fe_low_admin1,
    "aidtype_fe_growth_admin1_lowgov.tex",
    table_title = "Table 2B. FE Growth Models by Aid Type: Admin1, Low Governance"
)
save_and_show_table(
    fe_high_admin2,
    "aidtype_fe_growth_admin2_highgov.tex",
    table_title = "Table 2C. FE Growth Models by Aid Type: Admin2, High Governance"
)
save_and_show_table(
    fe_low_admin2,
    "aidtype_fe_growth_admin2_lowgov.tex",
    table_title = "Table 2D. FE Growth Models by Aid Type: Admin2, Low Governance"
)

# Control function
cfa_high_admin1 <- run_models_by_aid_type(
    high_admin1,
    aid_types,
    function(df) {
        perform_cfa_analysis(df, "GID_1", "nl_growth", "IV_lag", "GID_0")
    }
)
cfa_low_admin1 <- run_models_by_aid_type(
    low_admin1,
    aid_types,
    function(df) {
        perform_cfa_analysis(df, "GID_1", "nl_growth", "IV_lag", "GID_0")
    }
)
cfa_high_admin2 <- run_models_by_aid_type(
    high_admin2,
    aid_types,
    function(df) {
        perform_cfa_analysis(df, "GID_2", "nl_growth", "IV_lag", "GID_0")
    }
)
cfa_low_admin2 <- run_models_by_aid_type(
    low_admin2,
    aid_types,
    function(df) {
        perform_cfa_analysis(df, "GID_2", "nl_growth", "IV_lag", "GID_0")
    }
)

save_and_show_table(
    cfa_high_admin1,
    "aidtype_cfa_growth_admin1_highgov.tex",
    include_cfa = TRUE,
    table_title = "Table 3A. CFA Growth Models by Aid Type: Admin1, High Governance"
)
save_and_show_table(
    cfa_low_admin1,
    "aidtype_cfa_growth_admin1_lowgov.tex",
    include_cfa = TRUE,
    table_title = "Table 3B. CFA Growth Models by Aid Type: Admin1, Low Governance"
)
save_and_show_table(
    cfa_high_admin2,
    "aidtype_cfa_growth_admin2_highgov.tex",
    include_cfa = TRUE,
    table_title = "Table 3C. CFA Growth Models by Aid Type: Admin2, High Governance"
)
save_and_show_table(
    cfa_low_admin2,
    "aidtype_cfa_growth_admin2_lowgov.tex",
    include_cfa = TRUE,
    table_title = "Table 3D. CFA Growth Models by Aid Type: Admin2, Low Governance"
)
```

## 2) Interaction models with governance quality, by aid type (growth)

```{r interaction_growth, results='asis'}
interaction_ols_admin1 <- run_models_by_aid_type(
    panel_aid_admin1,
    aid_types,
    function(df) {
        perform_interaction_ols_analysis(df, "GID_1", "nl_growth", "GID_0")
    }
)
interaction_ols_admin2 <- run_models_by_aid_type(
    panel_aid_admin2,
    aid_types,
    function(df) {
        perform_interaction_ols_analysis(df, "GID_2", "nl_growth", "GID_0")
    }
)
interaction_fe_admin1 <- run_models_by_aid_type(
    panel_aid_admin1,
    aid_types,
    function(df) {
        perform_interaction_fe_analysis(df, "GID_1", "nl_growth", "GID_0")
    }
)
interaction_fe_admin2 <- run_models_by_aid_type(
    panel_aid_admin2,
    aid_types,
    function(df) {
        perform_interaction_fe_analysis(df, "GID_2", "nl_growth", "GID_0")
    }
)

save_and_show_table(
    interaction_ols_admin1,
    "aidtype_ols_interaction_growth_admin1.tex",
    include_interaction = TRUE,
    table_title = "Table 4A. OLS Interaction Models (Frag x Governance): Growth, Admin1"
)
save_and_show_table(
    interaction_ols_admin2,
    "aidtype_ols_interaction_growth_admin2.tex",
    include_interaction = TRUE,
    table_title = "Table 4B. OLS Interaction Models (Frag x Governance): Growth, Admin2"
)
save_and_show_table(
    interaction_fe_admin1,
    "aidtype_fe_interaction_growth_admin1.tex",
    include_interaction = TRUE,
    table_title = "Table 5A. FE Interaction Models (Frag x Governance): Growth, Admin1"
)
save_and_show_table(
    interaction_fe_admin2,
    "aidtype_fe_interaction_growth_admin2.tex",
    include_interaction = TRUE,
    table_title = "Table 5B. FE Interaction Models (Frag x Governance): Growth, Admin2"
)
```

## 3) Health-only analysis on U5M with high/low governance split

```{r health_u5m_split, results='asis'}
health_admin1 <- panel_aid_admin1 %>% filter(study_group == "health")
health_admin2 <- panel_aid_admin2 %>% filter(study_group == "health")

health_admin1_high <- health_admin1 %>% filter(high_gov == 1L)
health_admin1_low <- health_admin1 %>% filter(high_gov == 0L)
health_admin2_high <- health_admin2 %>% filter(high_gov == 1L)
health_admin2_low <- health_admin2 %>% filter(high_gov == 0L)

health_models_admin1 <- list(
    "OLS High Gov" = perform_ols_analysis(
        health_admin1_high,
        "GID_1",
        "u5m",
        "GID_0"
    ),
    "OLS Low Gov" = perform_ols_analysis(
        health_admin1_low,
        "GID_1",
        "u5m",
        "GID_0"
    ),
    "FE High Gov" = perform_fe_analysis(
        health_admin1_high,
        "GID_1",
        "u5m",
        "GID_0"
    ),
    "FE Low Gov" = perform_fe_analysis(
        health_admin1_low,
        "GID_1",
        "u5m",
        "GID_0"
    ),
    "CFA High Gov" = perform_cfa_analysis(
        health_admin1_high,
        "GID_1",
        "u5m",
        "IV_lag",
        "GID_0"
    ),
    "CFA Low Gov" = perform_cfa_analysis(
        health_admin1_low,
        "GID_1",
        "u5m",
        "IV_lag",
        "GID_0"
    )
)

health_models_admin2 <- list(
    "OLS High Gov" = perform_ols_analysis(
        health_admin2_high,
        "GID_2",
        "u5m",
        "GID_0"
    ),
    "OLS Low Gov" = perform_ols_analysis(
        health_admin2_low,
        "GID_2",
        "u5m",
        "GID_0"
    ),
    "FE High Gov" = perform_fe_analysis(
        health_admin2_high,
        "GID_2",
        "u5m",
        "GID_0"
    ),
    "FE Low Gov" = perform_fe_analysis(
        health_admin2_low,
        "GID_2",
        "u5m",
        "GID_0"
    ),
    "CFA High Gov" = perform_cfa_analysis(
        health_admin2_high,
        "GID_2",
        "u5m",
        "IV_lag",
        "GID_0"
    ),
    "CFA Low Gov" = perform_cfa_analysis(
        health_admin2_low,
        "GID_2",
        "u5m",
        "IV_lag",
        "GID_0"
    )
)

save_and_show_table(
    health_models_admin1,
    "health_u5m_split_admin1.tex",
    include_cfa = TRUE,
    table_title = "Table 6A. Health U5M Models by Governance Group: Admin1 (OLS, FE, CFA)"
)
save_and_show_table(
    health_models_admin2,
    "health_u5m_split_admin2.tex",
    include_cfa = TRUE,
    table_title = "Table 6B. Health U5M Models by Governance Group: Admin2 (OLS, FE, CFA)"
)
```

## 4) Health-only interaction models on U5M

```{r health_u5m_interaction, results='asis'}
health_interaction_models <- list(
    "Admin1 OLS Interaction" = perform_interaction_ols_analysis(
        health_admin1,
        "GID_1",
        "u5m",
        "GID_0"
    ),
    "Admin1 FE Interaction" = perform_interaction_fe_analysis(
        health_admin1,
        "GID_1",
        "u5m",
        "GID_0"
    ),
    "Admin2 OLS Interaction" = perform_interaction_ols_analysis(
        health_admin2,
        "GID_2",
        "u5m",
        "GID_0"
    ),
    "Admin2 FE Interaction" = perform_interaction_fe_analysis(
        health_admin2,
        "GID_2",
        "u5m",
        "GID_0"
    )
)

save_and_show_table(
    health_interaction_models,
    "health_u5m_interaction_models.tex",
    include_interaction = TRUE,
    landscape = TRUE,
    table_title = "Table 7. Health U5M Interaction Models (Frag x Governance): Admin1 and Admin2"
)
```

## 5) Governance stability diagnostics

```{r governance_stability_diagnostics}
raw_afro <- readr::read_csv(
    here::here(
        "00_rawdata",
        "ab_raw",
        "processed",
        "afrobarometer_w3_w6_geomerged_new.csv"
    ),
    show_col_types = FALSE
)

raw_obs_admin1 <- raw_afro %>%
    filter(!is.na(GID_1), !is.na(year), is.finite(sgqi)) %>%
    group_by(GID_1, year) %>%
    summarise(sgq_observed = mean(sgqi, na.rm = TRUE), .groups = "drop")

raw_obs_admin2 <- raw_afro %>%
    filter(!is.na(GID_2), !is.na(year), is.finite(sgqi)) %>%
    group_by(GID_2, year) %>%
    summarise(sgq_observed = mean(sgqi, na.rm = TRUE), .groups = "drop")

interp_admin1 <- panel_aid_admin1_fin %>%
    select(GID_1, year, mean_sgq_admin1) %>%
    distinct()

interp_admin2 <- panel_aid_admin2_fin %>%
    select(GID_2, year, mean_sgq_admin2) %>%
    distinct()

governance_stability <- bind_rows(
    compute_stability_metrics(
        raw_obs_admin1,
        "GID_1",
        "sgq_observed",
        "Observed Afro years - admin1"
    ),
    compute_stability_metrics(
        raw_obs_admin2,
        "GID_2",
        "sgq_observed",
        "Observed Afro years - admin2"
    ),
    compute_stability_metrics(
        interp_admin1,
        "GID_1",
        "mean_sgq_admin1",
        "Interpolated panel years - admin1"
    ),
    compute_stability_metrics(
        interp_admin2,
        "GID_2",
        "mean_sgq_admin2",
        "Interpolated panel years - admin2"
    )
)

readr::write_csv(
    governance_stability,
    here::here(
        "03_output",
        "tabs",
        paste0("governance_stability_metrics", output_suffix, ".csv")
    )
)

knitr::kable(governance_stability, digits = 4)
```

### Methods note
- Carry-forward and bounded-trend governance paths are assumptions, not direct observations.
- Baseline models keep the interpolated governance panel as the primary specification.
- Sensitivity models below report whether main coefficients are stable when governance paths are changed.
- Baseline causal interpretation remains anchored to the observed-governance panel window unless robustness is consistent.

## 6) Governance sensitivity models

```{r governance_sensitivity_models, results='asis'}
gov_paths_admin1 <- build_governance_paths(
    panel_aid_admin1,
    "GID_1",
    raw_obs_admin1
)
gov_paths_admin2 <- build_governance_paths(
    panel_aid_admin2,
    "GID_2",
    raw_obs_admin2
)

health_admin1_sens <- health_admin1 %>%
    left_join(gov_paths_admin1, by = c("GID_1", "year"))

health_admin2_sens <- health_admin2 %>%
    left_join(gov_paths_admin2, by = c("GID_2", "year"))

sensitivity_models_admin1 <- list(
    "Baseline (Interpolated SGQ)" = run_variant_interaction(
        health_admin1_sens,
        "GID_1",
        "u5m",
        "GID_0",
        "lag_gov_baseline"
    ),
    "Alternative A: Carry-forward SGQ" = run_variant_interaction(
        health_admin1_sens,
        "GID_1",
        "u5m",
        "GID_0",
        "lag_gov_cf"
    ),
    "Alternative B: Bounded-trend SGQ" = run_variant_interaction(
        health_admin1_sens,
        "GID_1",
        "u5m",
        "GID_0",
        "lag_gov_trend"
    )
)

sensitivity_models_admin2 <- list(
    "Baseline (Interpolated SGQ)" = run_variant_interaction(
        health_admin2_sens,
        "GID_2",
        "u5m",
        "GID_0",
        "lag_gov_baseline"
    ),
    "Alternative A: Carry-forward SGQ" = run_variant_interaction(
        health_admin2_sens,
        "GID_2",
        "u5m",
        "GID_0",
        "lag_gov_cf"
    ),
    "Alternative B: Bounded-trend SGQ" = run_variant_interaction(
        health_admin2_sens,
        "GID_2",
        "u5m",
        "GID_0",
        "lag_gov_trend"
    )
)

save_and_show_table(
    sensitivity_models_admin1,
    "health_u5m_governance_sensitivity_admin1.tex",
    include_interaction = TRUE,
    table_title = "Table 8A. Health U5M governance sensitivity models: Admin1"
)

save_and_show_table(
    sensitivity_models_admin2,
    "health_u5m_governance_sensitivity_admin2.tex",
    include_interaction = TRUE,
    table_title = "Table 8B. Health U5M governance sensitivity models: Admin2"
)

sensitivity_terms <- bind_rows(
    collect_sensitivity_terms(sensitivity_models_admin1, "Admin1"),
    collect_sensitivity_terms(sensitivity_models_admin2, "Admin2")
)

readr::write_csv(
    sensitivity_terms,
    here::here(
        "03_output",
        "tabs",
        paste0("governance_sensitivity_terms", output_suffix, ".csv")
    )
)

knitr::kable(sensitivity_terms, digits = 4)

if (!any(c(panel_aid_admin1$year, panel_aid_admin2$year) > 2015)) {
    cat(
        "\nPost-2015 outcomes are not currently present in this analysis panel. "
    )
    cat(
        "Sensitivity models therefore compare governance path assumptions within the observed panel window.\n"
    )
}
```

## 7) FE fallback log

```{r fe_fallback_report}
if (nrow(fe_fallback_log) == 0) {
    cat("No FE fallback events were triggered.")
} else {
    fe_fallback_log %>%
        arrange(context, admin_level) %>%
        knitr::kable(digits = 3)
}
```
