---
title: "Fragmentation, Capacity, and Lag Strategy"
author: "Ethan Sager"
format:
  html:
    toc: true
    code-fold: true
execute:
  echo: false
  message: false
  warning: false
---

## Why This File Exists

This file implements the exact identification and interpretation workflow we discussed:

1. Use **pre-determined baseline governance capacity** as the moderator.
2. Estimate the moderation model first on **overall data**, then by **sector**, for both admin levels.
3. Run **lag sensitivity** over candidate values of `t`.
4. Report interpretable quantities:
- marginal effect of fragmentation at capacity `p25`, `p50`, `p75`
- sign-switch threshold
- placebo model with future fragmentation

```{r setup}
if (!requireNamespace("pacman", quietly = TRUE)) {
    install.packages("pacman")
}

pacman::p_load(
    tidyverse,
    here,
    readr,
    fixest,
    broom,
    knitr
)

options(scipen = 999)

# -----------------------------------------------------------------------------
# Configuration
# -----------------------------------------------------------------------------

# Default execution target is the 2000-2020 five-year panel.
panel_suffix <- "_5year_2000_2020"
lag_t <- 1L
growth_requires_full_windows <- TRUE

window_label <- if_else(str_detect(panel_suffix, "_5year"), "5-year", "annual")
window_years <- if_else(str_detect(panel_suffix, "_5year"), 5L, 1L)

# Keep lag grid explicit even when fixed to one value.
candidate_t <- unique(as.integer(lag_t))

# Baseline year for predetermined capacity moderator.
baseline_year <- if_else(panel_suffix == "_5year_2000_2020", 2000L, 2005L)

output_dir <- here::here("03_output", "tabs")
dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)

read_panel_csv <- function(file_stub) {
    file_path <- here::here(
        "01_panel_data",
        paste0(file_stub, panel_suffix, ".csv")
    )
    if (!file.exists(file_path)) {
        stop("Missing panel data file: ", file_path)
    }
    readr::read_csv(file_path, show_col_types = FALSE)
}

overall_admin1 <- read_panel_csv("panel_aid_admin1_fin")
overall_admin2 <- read_panel_csv("panel_aid_admin2_fin")
sector_admin1 <- read_panel_csv("panel_aid_admin1_by_sector")
sector_admin2 <- read_panel_csv("panel_aid_admin2_by_sector")

admin_specs <- list(
    admin1 = list(
        admin_label = "Admin1",
        admin_id = "GID_1",
        frag_var = "frag_index_admin1",
        pop_var = "ln_pop_admin1",
        aid_var = "total_aid_admin1",
        sgq_var = "mean_sgq_admin1",
        overall_data = overall_admin1,
        sector_data = sector_admin1
    ),
    admin2 = list(
        admin_label = "Admin2",
        admin_id = "GID_2",
        frag_var = "frag_index_admin2",
        pop_var = "ln_pop_admin2",
        aid_var = "total_aid_admin2",
        sgq_var = "mean_sgq_admin2",
        overall_data = overall_admin2,
        sector_data = sector_admin2
    )
)

safe_num <- function(x, fn = c("mean", "median", "min", "max")) {
    fn <- match.arg(fn)
    x <- x[is.finite(x)]
    if (length(x) == 0) {
        return(NA_real_)
    }
    switch(fn, mean = mean(x), median = median(x), min = min(x), max = max(x))
}

safe_quantile <- function(x, prob) {
    x <- x[is.finite(x)]
    if (length(x) == 0) {
        return(NA_real_)
    }
    as.numeric(quantile(x, probs = prob, na.rm = TRUE))
}

get_term_name <- function(model, candidates) {
    found <- intersect(candidates, names(coef(model)))
    if (length(found) == 0) {
        return(NA_character_)
    }
    found[[1]]
}

has_within_time_variation <- function(
    data,
    admin_id,
    required_vars = character(0)
) {
    d <- data
    if (length(required_vars) > 0) {
        d <- d %>%
            filter(if_all(all_of(required_vars), ~ !is.na(.x) & is.finite(.x)))
    }

    counts <- d %>%
        distinct(.data[[admin_id]], year) %>%
        count(.data[[admin_id]], name = "n_years")

    if (nrow(counts) == 0) {
        return(FALSE)
    }

    any(counts$n_years >= 2)
}

fe_fallback_log <- tibble(
    stage = character(),
    admin = character(),
    t = integer(),
    fe_term = character(),
    n_obs = integer(),
    min_year = double(),
    max_year = double()
)

resolve_fe_term <- function(
    data,
    admin_id,
    required_vars,
    admin_label,
    t_lag,
    stage
) {
    if (has_within_time_variation(data, admin_id, required_vars)) {
        return(paste0("GID_0^year + ", admin_id))
    }

    fe_fallback_log <<- bind_rows(
        fe_fallback_log,
        tibble(
            stage = stage,
            admin = admin_label,
            t = t_lag,
            fe_term = "GID_0",
            n_obs = nrow(data),
            min_year = suppressWarnings(min(data$year, na.rm = TRUE)),
            max_year = suppressWarnings(max(data$year, na.rm = TRUE))
        )
    ) %>%
        distinct()

    "GID_0"
}

build_baseline_capacity <- function(data, admin_id, sgq_var, baseline_year) {
    lookup <- data %>%
        select(unit_id = all_of(admin_id), year, sgq = all_of(sgq_var)) %>%
        distinct() %>%
        arrange(unit_id, year) %>%
        group_by(unit_id) %>%
        summarise(
            cap_base = mean(sgq[year == baseline_year], na.rm = TRUE),
            cap_first = sgq[which(is.finite(sgq))[1]],
            .groups = "drop"
        ) %>%
        mutate(
            cap_base = if_else(is.finite(cap_base), cap_base, cap_first)
        ) %>%
        select(unit_id, cap_base)

    lookup
}

prepare_lagged_data <- function(
    data,
    spec,
    t_lag,
    baseline_year,
    outcome_var = "mean_nl",
    require_full_windows = growth_requires_full_windows
) {
    admin_id <- spec$admin_id
    group_vars <- admin_id
    if ("study_group" %in% names(data)) {
        group_vars <- c(group_vars, "study_group")
    }

    outcome_col <- if (outcome_var %in% names(data)) {
        outcome_var
    } else if ("mean" %in% names(data)) {
        "mean"
    } else if ("mean_nl" %in% names(data)) {
        "mean_nl"
    } else {
        stop(
            "Outcome column not found. Expected one of: ",
            outcome_var,
            ", mean, mean_nl"
        )
    }

    baseline_lookup <- build_baseline_capacity(
        data,
        admin_id,
        spec$sgq_var,
        baseline_year
    )

    if (!("period_years" %in% names(data))) {
        data <- data %>% mutate(period_years = as.numeric(window_years))
    }

    growth_denom <- if (window_years == 5L) {
        as.numeric(window_years * t_lag)
    } else {
        as.numeric(t_lag)
    }

    d <- data %>%
        left_join(baseline_lookup, by = setNames("unit_id", admin_id)) %>%
        arrange(across(all_of(group_vars)), year) %>%
        group_by(across(all_of(group_vars))) %>%
        mutate(
            y_lag = dplyr::lag(.data[[outcome_col]], n = t_lag),
            lag_period_years = dplyr::lag(period_years, n = t_lag),
            growth = 100 *
                (log(.data[[outcome_col]] + 0.01) - log(y_lag + 0.01)) /
                growth_denom,
            frag_lag = dplyr::lag(.data[[spec$frag_var]], n = t_lag),
            aid_lag = log(dplyr::lag(.data[[spec$aid_var]], n = t_lag) + 0.01),
            pop_lag = dplyr::lag(.data[[spec$pop_var]], n = t_lag),
            gov_lag = dplyr::lag(.data[[spec$sgq_var]], n = t_lag),
            frag_lead = dplyr::lead(.data[[spec$frag_var]], n = t_lag)
        ) %>%
        ungroup() %>%
        mutate(
            cap_med = median(cap_base, na.rm = TRUE),
            cap_c = cap_base - cap_med
        ) %>%
        filter(
            is.finite(growth),
            is.finite(frag_lag),
            is.finite(aid_lag),
            is.finite(pop_lag),
            is.finite(cap_c)
        )

    if (isTRUE(require_full_windows) && "period_years" %in% names(d)) {
        d <- d %>%
            filter(
                period_years == window_years,
                lag_period_years == window_years
            )
    }

    d
}

fit_main_model <- function(data, spec, t_lag, stage = "overall") {
    d <- prepare_lagged_data(data, spec, t_lag, baseline_year)

    fe_term <- resolve_fe_term(
        data = d,
        admin_id = spec$admin_id,
        required_vars = c("growth", "frag_lag", "cap_c", "aid_lag", "pop_lag"),
        admin_label = spec$admin_label,
        t_lag = t_lag,
        stage = stage
    )

    model <- fixest::feols(
        as.formula(paste0(
            "growth ~ frag_lag * cap_c + aid_lag + pop_lag | ",
            fe_term
        )),
        cluster = ~GID_0,
        data = d
    )

    list(
        model = model,
        data = d,
        fe_term = fe_term,
        t = t_lag,
        admin = spec$admin_label,
        stage = stage
    )
}

fit_timevarying_model <- function(data, spec, t_lag, stage = "overall_timevarying") {
    d <- prepare_lagged_data(data, spec, t_lag, baseline_year) %>%
        filter(is.finite(gov_lag)) %>%
        mutate(
            gov_lag_c = gov_lag - median(gov_lag, na.rm = TRUE)
        )

    fe_term <- resolve_fe_term(
        data = d,
        admin_id = spec$admin_id,
        required_vars = c(
            "growth",
            "frag_lag",
            "gov_lag_c",
            "aid_lag",
            "pop_lag"
        ),
        admin_label = spec$admin_label,
        t_lag = t_lag,
        stage = stage
    )

    model <- fixest::feols(
        as.formula(paste0(
            "growth ~ frag_lag * gov_lag_c + aid_lag + pop_lag | ",
            fe_term
        )),
        cluster = ~GID_0,
        data = d
    )

    list(
        model = model,
        data = d,
        fe_term = fe_term,
        t = t_lag,
        admin = spec$admin_label,
        stage = stage
    )
}

extract_main_metrics <- function(fit_obj) {
    model <- fit_obj$model
    d <- fit_obj$data

    frag_name <- get_term_name(model, c("frag_lag"))
    int_name <- get_term_name(model, c("frag_lag:cap_c", "cap_c:frag_lag"))

    ct <- fixest::coeftable(model)
    interaction_est <- if (!is.na(int_name)) ct[int_name, 1] else NA_real_
    interaction_se <- if (!is.na(int_name)) ct[int_name, 2] else NA_real_
    interaction_p <- if (!is.na(int_name)) ct[int_name, 4] else NA_real_

    tibble(
        stage = fit_obj$stage,
        admin = fit_obj$admin,
        t = fit_obj$t,
        fe_term = fit_obj$fe_term,
        n_obs = nobs(model),
        n_units = n_distinct(d[[if_else(
            fit_obj$admin == "Admin1",
            "GID_1",
            "GID_2"
        )]]),
        year_min = safe_num(d$year, "min"),
        year_max = safe_num(d$year, "max"),
        interaction_estimate = interaction_est,
        interaction_se = interaction_se,
        interaction_p = interaction_p,
        interaction_t = interaction_est / interaction_se,
        r2_within = as.numeric(fixest::fitstat(model, "wr2"))
    )
}

marginal_effects_at_quantiles <- function(fit_obj) {
    model <- fit_obj$model
    d <- fit_obj$data

    frag_name <- get_term_name(model, c("frag_lag"))
    int_name <- get_term_name(model, c("frag_lag:cap_c", "cap_c:frag_lag"))

    if (is.na(frag_name) || is.na(int_name)) {
        return(tibble())
    }

    b <- coef(model)
    V <- vcov(model)

    cap_q <- quantile(d$cap_base, probs = c(0.25, 0.50, 0.75), na.rm = TRUE)
    cap_med <- median(d$cap_base, na.rm = TRUE)

    map_dfr(seq_along(cap_q), function(i) {
        q_lab <- names(cap_q)[i]
        cap_raw <- as.numeric(cap_q[i])
        cap_c <- cap_raw - cap_med

        me <- b[[frag_name]] + b[[int_name]] * cap_c
        se <- sqrt(
            V[frag_name, frag_name] +
                cap_c^2 * V[int_name, int_name] +
                2 * cap_c * V[frag_name, int_name]
        )

        tibble(
            stage = fit_obj$stage,
            admin = fit_obj$admin,
            t = fit_obj$t,
            quantile = q_lab,
            capacity_value = cap_raw,
            frag_marginal_effect = me,
            std_error = se,
            conf_low = me - 1.96 * se,
            conf_high = me + 1.96 * se
        )
    })
}

sign_switch_threshold <- function(fit_obj) {
    model <- fit_obj$model
    d <- fit_obj$data

    frag_name <- get_term_name(model, c("frag_lag"))
    int_name <- get_term_name(model, c("frag_lag:cap_c", "cap_c:frag_lag"))

    if (is.na(frag_name) || is.na(int_name)) {
        return(tibble())
    }

    b <- coef(model)
    cap_med <- median(d$cap_base, na.rm = TRUE)

    if (!is.finite(b[[int_name]]) || abs(b[[int_name]]) < 1e-10) {
        cap_star <- NA_real_
    } else {
        cap_star <- cap_med - b[[frag_name]] / b[[int_name]]
    }

    tibble(
        stage = fit_obj$stage,
        admin = fit_obj$admin,
        t = fit_obj$t,
        cap_threshold = cap_star
    )
}

marginal_effect_curve <- function(fit_obj, n_points = 100L) {
    model <- fit_obj$model
    d <- fit_obj$data

    frag_name <- get_term_name(model, c("frag_lag"))
    int_name <- get_term_name(model, c("frag_lag:cap_c", "cap_c:frag_lag"))

    if (is.na(frag_name) || is.na(int_name)) {
        return(tibble())
    }

    b <- coef(model)
    V <- vcov(model)
    cap_med <- median(d$cap_base, na.rm = TRUE)

    cap_grid <- seq(
        quantile(d$cap_base, 0.05, na.rm = TRUE),
        quantile(d$cap_base, 0.95, na.rm = TRUE),
        length.out = n_points
    )

    map_dfr(cap_grid, function(cap_raw) {
        cap_c <- cap_raw - cap_med
        me <- b[[frag_name]] + b[[int_name]] * cap_c
        se <- sqrt(
            V[frag_name, frag_name] +
                cap_c^2 * V[int_name, int_name] +
                2 * cap_c * V[frag_name, int_name]
        )

        tibble(
            stage = fit_obj$stage,
            admin = fit_obj$admin,
            t = fit_obj$t,
            capacity_value = cap_raw,
            frag_marginal_effect = me,
            conf_low = me - 1.96 * se,
            conf_high = me + 1.96 * se
        )
    })
}

fit_placebo <- function(data, spec, t_lag) {
    d <- prepare_lagged_data(data, spec, t_lag, baseline_year) %>%
        filter(is.finite(frag_lead))

    fe_term <- resolve_fe_term(
        data = d,
        admin_id = spec$admin_id,
        required_vars = c("growth", "frag_lead", "cap_c", "aid_lag", "pop_lag"),
        admin_label = spec$admin_label,
        t_lag = t_lag,
        stage = "placebo"
    )

    model <- fixest::feols(
        as.formula(paste0(
            "growth ~ frag_lead * cap_c + aid_lag + pop_lag | ",
            fe_term
        )),
        cluster = ~GID_0,
        data = d
    )

    int_name <- get_term_name(model, c("frag_lead:cap_c", "cap_c:frag_lead"))
    ct <- fixest::coeftable(model)

    tibble(
        admin = spec$admin_label,
        t = t_lag,
        n_obs = nobs(model),
        placebo_interaction = if (!is.na(int_name)) {
            ct[int_name, 1]
        } else {
            NA_real_
        },
        placebo_se = if (!is.na(int_name)) ct[int_name, 2] else NA_real_,
        placebo_p = if (!is.na(int_name)) ct[int_name, 4] else NA_real_,
        fe_term = fe_term
    )
}

choose_recommended_t <- function(overall_metrics, candidate_t, panel_suffix) {
    if (str_detect(panel_suffix, "_5year")) {
        return(list(
            t = 1L,
            reason = "5-year panel has very limited periods; t=1 is the only defensible baseline."
        ))
    }

    agg <- overall_metrics %>%
        filter(stage == "overall") %>%
        group_by(t) %>%
        summarise(
            mean_n = mean(n_obs, na.rm = TRUE),
            mean_abs_t = mean(abs(interaction_t), na.rm = TRUE),
            .groups = "drop"
        ) %>%
        mutate(retention = mean_n / max(mean_n, na.rm = TRUE))

    eligible <- agg %>% filter(retention >= 0.70)
    if (nrow(eligible) == 0) {
        return(list(
            t = min(candidate_t),
            reason = "No lag retained >=70% of baseline sample; defaulting to shortest lag."
        ))
    }

    best <- eligible %>%
        arrange(desc(mean_abs_t), t) %>%
        slice(1)

    list(
        t = best$t[[1]],
        reason = paste0(
            "Selected t=",
            best$t[[1]],
            " maximizing signal among lags with >=70% sample retention."
        )
    )
}

governance_status_summary <- function(data, admin_label) {
    if (!("sgq_status" %in% names(data))) {
        return(tibble(
            admin = admin_label,
            status = "missing_status_column",
            share = NA_real_,
            n = NA_integer_
        ))
    }

    data %>%
        mutate(sgq_status = as.character(sgq_status)) %>%
        count(sgq_status, name = "n") %>%
        mutate(
            admin = admin_label,
            share = n / sum(n, na.rm = TRUE)
        ) %>%
        rename(status = sgq_status) %>%
        select(admin, status, share, n)
}

governance_stability_metrics <- function(data, spec) {
    admin_id <- spec$admin_id
    sgq_var <- spec$sgq_var

    lag_df <- data %>%
        select(unit = all_of(admin_id), year, sgq = all_of(sgq_var), sgq_status) %>%
        arrange(unit, year) %>%
        group_by(unit) %>%
        mutate(
            lag_sgq = dplyr::lag(sgq),
            lag_status = dplyr::lag(sgq_status),
            abs_change = abs(sgq - lag_sgq)
        ) %>%
        ungroup()

    unit_slopes <- data %>%
        select(unit = all_of(admin_id), year, sgq = all_of(sgq_var)) %>%
        filter(is.finite(sgq)) %>%
        group_by(unit) %>%
        summarise(
            n = n(),
            slope = if_else(
                n >= 2,
                coef(lm(sgq ~ year))[["year"]],
                NA_real_
            ),
            .groups = "drop"
        )

    observed_pairs <- lag_df %>%
        filter(
            is.finite(sgq),
            is.finite(lag_sgq),
            sgq_status == "observed",
            lag_status == "observed"
        )

    tibble(
        admin = spec$admin_label,
        n_units = n_distinct(data[[admin_id]]),
        n_rows = nrow(data),
        lag_corr = cor(
            lag_df$sgq,
            lag_df$lag_sgq,
            use = "pairwise.complete.obs"
        ),
        slope_p10 = safe_quantile(unit_slopes$slope, 0.10),
        slope_p50 = safe_quantile(unit_slopes$slope, 0.50),
        slope_p90 = safe_quantile(unit_slopes$slope, 0.90),
        share_small_abs_change_observed = mean(
            observed_pairs$abs_change <= 0.10,
            na.rm = TRUE
        )
    )
}

window_drop_diagnostics <- function(spec, t_lag) {
    unrestricted <- prepare_lagged_data(
        data = spec$overall_data,
        spec = spec,
        t_lag = t_lag,
        baseline_year = baseline_year,
        require_full_windows = FALSE
    )

    restricted <- prepare_lagged_data(
        data = spec$overall_data,
        spec = spec,
        t_lag = t_lag,
        baseline_year = baseline_year,
        require_full_windows = TRUE
    )

    tibble(
        admin = spec$admin_label,
        t = t_lag,
        n_unrestricted = nrow(unrestricted),
        n_full_windows = nrow(restricted),
        share_dropped = if_else(
            n_unrestricted > 0,
            1 - n_full_windows / n_unrestricted,
            NA_real_
        )
    )
}
```

## Data support and lag candidates

```{r data_support}
support_table <- tibble(
    dataset = c(
        "overall_admin1",
        "overall_admin2",
        "sector_admin1",
        "sector_admin2"
    ),
    rows = c(
        nrow(overall_admin1),
        nrow(overall_admin2),
        nrow(sector_admin1),
        nrow(sector_admin2)
    ),
    years = c(
        paste(sort(unique(overall_admin1$year)), collapse = ", "),
        paste(sort(unique(overall_admin2$year)), collapse = ", "),
        paste(sort(unique(sector_admin1$year)), collapse = ", "),
        paste(sort(unique(sector_admin2$year)), collapse = ", ")
    )
)

kable(support_table)
cat("\nCandidate lag t:", paste(candidate_t, collapse = ", "), "\n")
cat("\nBaseline capacity year:", baseline_year, "\n")

status_diag <- bind_rows(
    governance_status_summary(overall_admin1, "Admin1"),
    governance_status_summary(overall_admin2, "Admin2")
)

stability_diag <- bind_rows(
    governance_stability_metrics(overall_admin1, admin_specs$admin1),
    governance_stability_metrics(overall_admin2, admin_specs$admin2)
)

window_diag <- bind_rows(
    window_drop_diagnostics(admin_specs$admin1, candidate_t[[1]]),
    window_drop_diagnostics(admin_specs$admin2, candidate_t[[1]])
)

readr::write_csv(
    status_diag,
    here::here(
        "03_output",
        "tabs",
        paste0("lag_strategy_governance_status", panel_suffix, ".csv")
    )
)
readr::write_csv(
    stability_diag,
    here::here(
        "03_output",
        "tabs",
        paste0("lag_strategy_governance_metrics", panel_suffix, ".csv")
    )
)
readr::write_csv(
    window_diag,
    here::here(
        "03_output",
        "tabs",
        paste0("lag_strategy_window_diagnostics", panel_suffix, ".csv")
    )
)

cat("\nGovernance status composition\n")
kable(status_diag, digits = 4)
cat("\nGovernance stability metrics\n")
kable(stability_diag, digits = 4)
cat("\nWindow diagnostics (full-window filter impact)\n")
kable(window_diag, digits = 4)
```

## Step 1: Overall models across lag choices

```{r overall_lag_grid}
overall_fits <- list()
overall_metrics <- list()
overall_marginals <- list()
overall_thresholds <- list()
overall_curves <- list()

for (nm in names(admin_specs)) {
    spec <- admin_specs[[nm]]
    for (t_lag in candidate_t) {
        fit_obj <- fit_main_model(
            data = spec$overall_data,
            spec = spec,
            t_lag = t_lag,
            stage = "overall"
        )

        key <- paste(spec$admin_label, "t", t_lag, sep = "_")
        overall_fits[[key]] <- fit_obj
        overall_metrics[[key]] <- extract_main_metrics(fit_obj)
        overall_marginals[[key]] <- marginal_effects_at_quantiles(fit_obj)
        overall_thresholds[[key]] <- sign_switch_threshold(fit_obj)
        overall_curves[[key]] <- marginal_effect_curve(fit_obj)
    }
}

overall_metrics_df <- bind_rows(overall_metrics)
overall_marginals_df <- bind_rows(overall_marginals)
overall_thresholds_df <- bind_rows(overall_thresholds)
overall_curves_df <- bind_rows(overall_curves)

readr::write_csv(
    overall_metrics_df,
    here::here(
        "03_output",
        "tabs",
        paste0("lag_strategy_overall_metrics", panel_suffix, ".csv")
    )
)
readr::write_csv(
    overall_marginals_df,
    here::here(
        "03_output",
        "tabs",
        paste0("lag_strategy_overall_marginals", panel_suffix, ".csv")
    )
)
readr::write_csv(
    overall_thresholds_df,
    here::here(
        "03_output",
        "tabs",
        paste0("lag_strategy_overall_thresholds", panel_suffix, ".csv")
    )
)

kable(overall_metrics_df, digits = 4)
```

## Step 2: Select a reasonable `t`

```{r choose_t}
lag_choice <- choose_recommended_t(
    overall_metrics_df,
    candidate_t,
    panel_suffix
)
recommended_t <- lag_choice$t

cat("Recommended t =", recommended_t, "\n")
cat("Reason:", lag_choice$reason, "\n")

# Also show plain retention and interaction signal by lag.
lag_scorecard <- overall_metrics_df %>%
    group_by(t) %>%
    summarise(
        mean_n_obs = mean(n_obs, na.rm = TRUE),
        mean_abs_interaction_t = mean(abs(interaction_t), na.rm = TRUE),
        mean_interaction_p = mean(interaction_p, na.rm = TRUE),
        .groups = "drop"
    ) %>%
    mutate(retention_vs_best = mean_n_obs / max(mean_n_obs, na.rm = TRUE))

kable(lag_scorecard, digits = 4)
```

## Step 3: Interpretable moderation outputs (overall, recommended `t`)

```{r interpret_overall}
overall_metrics_t <- overall_metrics_df %>%
    filter(t == recommended_t)

overall_marginals_t <- overall_marginals_df %>%
    filter(t == recommended_t)

overall_thresholds_t <- overall_thresholds_df %>%
    filter(t == recommended_t)

cat("### Model summary at recommended lag\n")
kable(overall_metrics_t, digits = 4)
cat("\n### Fragmentation marginal effects at capacity quantiles\n")
kable(overall_marginals_t, digits = 4)
cat("\n### Sign-switch capacity threshold\n")
kable(overall_thresholds_t, digits = 4)
```

```{r marginal_effect_plot, fig.height=5, fig.width=9}
plot_data <- overall_curves_df %>%
    filter(t == recommended_t)

ggplot(
    plot_data,
    aes(
        x = capacity_value,
        y = frag_marginal_effect,
        color = admin,
        fill = admin
    )
) +
    geom_ribbon(
        aes(ymin = conf_low, ymax = conf_high),
        alpha = 0.15,
        color = NA
    ) +
    geom_line(linewidth = 1) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    labs(
        title = paste0(
            "Marginal effect of fragmentation by baseline capacity (",
            window_label,
            ")"
        ),
        subtitle = paste0("Recommended lag t = ", recommended_t),
        x = "Baseline capacity",
        y = "d(growth)/d(fragmentation)"
    ) +
    theme_minimal(base_size = 12)
```

## Step 3B: Sensitivity moderator (lagged time-varying governance)

```{r lagged_governance_sensitivity}
extract_timevarying_terms <- function(fit_obj) {
    model <- fit_obj$model
    ct <- fixest::coeftable(model)
    int_name <- get_term_name(model, c("frag_lag:gov_lag_c", "gov_lag_c:frag_lag"))
    frag_name <- get_term_name(model, c("frag_lag"))

    tibble(
        admin = fit_obj$admin,
        t = fit_obj$t,
        n_obs = nobs(model),
        fe_term = fit_obj$fe_term,
        frag_estimate = if (!is.na(frag_name)) ct[frag_name, 1] else NA_real_,
        frag_se = if (!is.na(frag_name)) ct[frag_name, 2] else NA_real_,
        interaction_estimate = if (!is.na(int_name)) ct[int_name, 1] else NA_real_,
        interaction_se = if (!is.na(int_name)) ct[int_name, 2] else NA_real_,
        interaction_p = if (!is.na(int_name)) ct[int_name, 4] else NA_real_
    )
}

timevarying_fits <- list(
    fit_timevarying_model(
        admin_specs$admin1$overall_data,
        admin_specs$admin1,
        recommended_t
    ),
    fit_timevarying_model(
        admin_specs$admin2$overall_data,
        admin_specs$admin2,
        recommended_t
    )
)

timevarying_terms <- bind_rows(lapply(timevarying_fits, extract_timevarying_terms))

readr::write_csv(
    timevarying_terms,
    here::here(
        "03_output",
        "tabs",
        paste0("lag_strategy_timevarying_sensitivity", panel_suffix, ".csv")
    )
)

kable(timevarying_terms, digits = 4)
```

## Step 4: Sector models at recommended `t`

```{r sector_models}
sector_results <- list()
sector_marginals <- list()

for (nm in names(admin_specs)) {
    spec <- admin_specs[[nm]]
    sectors <- sort(unique(spec$sector_data$study_group))

    for (sec in sectors) {
        sec_data <- spec$sector_data %>% filter(study_group == sec)

        fit_obj <- tryCatch(
            fit_main_model(sec_data, spec, recommended_t, stage = "sector"),
            error = function(e) NULL
        )

        if (is.null(fit_obj)) {
            next
        }

        key <- paste(spec$admin_label, sec, sep = "_")
        sector_results[[key]] <- extract_main_metrics(fit_obj) %>%
            mutate(study_group = sec)
        sector_marginals[[key]] <- marginal_effects_at_quantiles(fit_obj) %>%
            mutate(study_group = sec)
    }
}

sector_results_df <- bind_rows(sector_results) %>%
    select(study_group, everything())

sector_marginals_df <- bind_rows(sector_marginals) %>%
    select(study_group, everything())

readr::write_csv(
    sector_results_df,
    here::here(
        "03_output",
        "tabs",
        paste0(
            "lag_strategy_sector_metrics_t",
            recommended_t,
            panel_suffix,
            ".csv"
        )
    )
)
readr::write_csv(
    sector_marginals_df,
    here::here(
        "03_output",
        "tabs",
        paste0(
            "lag_strategy_sector_marginals_t",
            recommended_t,
            panel_suffix,
            ".csv"
        )
    )
)

kable(sector_results_df, digits = 4)
```

## Step 5: Placebo test (future fragmentation)

```{r placebo_test}
placebo_df <- bind_rows(
    fit_placebo(
        admin_specs$admin1$overall_data,
        admin_specs$admin1,
        recommended_t
    ),
    fit_placebo(
        admin_specs$admin2$overall_data,
        admin_specs$admin2,
        recommended_t
    )
)

readr::write_csv(
    placebo_df,
    here::here(
        "03_output",
        "tabs",
        paste0("lag_strategy_placebo", panel_suffix, ".csv")
    )
)

kable(placebo_df, digits = 4)
```

## FE fallback log

```{r fe_fallback}
if (nrow(fe_fallback_log) == 0) {
    cat("No FE fallback events were triggered.")
} else {
    kable(fe_fallback_log, digits = 3)
}
```

## Advisor note on a reasonable `t`

- If this is **annual data**, use `t=1` as baseline for identification and interpretability, and treat `t=2,3` as persistence checks.
- If this is **5-year data**, `t=1` is effectively a 5-year lag and is the practical baseline.
- In the 2000-2020 five-year design, primary growth models drop transitions involving the singleton 2020 bucket.
- A "reasonable" `t` is the one that balances:
  - signal (interaction effect not vanishing)
  - sample retention
  - temporal plausibility for the outcome mechanism

This file gives all three directly so you can defend your choice in the chapter.
